---
title: "Volatility"
author: "Nathan J. Tuttle"
date: "March 22, 2017"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lecture Assignment
Half of you will be assigned to find a series that is less volatile than the S&P 500, the other half a series that is more volatile.
Download the data.

### *Calculate log returns.*
```{r Log returns}

library(tseries)

snpData<- get.hist.quote('^gspc',quote='Close')

snpPret<-log(lag(snpData)) - log(snpData)

snpPret
```

### Calculate volatility measure.
```{r Volatility measure}

#Volatility
SNVol <- sd(snpPret) * sqrt(250) *100

Vol<- function(d,logrets)
{
  var=0
  lam=0
  varlist<-NULL
  for(r in logrets)
  {
    lam=lam*(1- 1/d) +1
    var = (1 - 1/lam)*var + (1/lam)*r^2
      varlist<- c(varlist,var)
  }
  sqrt(varlist)
}
```
### Calculate volatility over entire length of series for various three different decay factors.
```{r Volatility over length with 3 Different Decay Factors}

```

### Plot the results, overlaying the volatility curves on the data, just as was done in the S&P example.
```{r Plotted Results}

```

# Deliverable
*Upload the Markdown file containing your code, analysis, and discussion to GitHub. Post a link to the Markdown file in the space below.
The markdown document should have code for entering the data, calculating log returns, calculating volatility measure, and calculating volatility for the entire series using three different decay factors.
Also needs to have code for a plot (and the plot itself) with the data and volatility overlaid.
The discussion board will talk about the differences in the volatility plots for different stocks.
*


